Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
App Engine costs.
Threat model.

Censor allows www.google.com (or an IP); forbids appspot.com.

@@

>>>>

The censor is able to inspect all traffic that passes through
the censorship boundary and block or allow it at will.
The censor is able to actively scan for proxies, and issue followup
connections to hosts that clients connect to, in order to determine
whether they are proxies.
The censor may block the web host on which the reflector web app runs,
but it must allow access to some domain that can front for it.
In our deployment using App Engine, the censor may block appspot.com,
but must allow www.google.com (or its IP address, or some other domain
that goes through the frontend server).

The censor must operate at line rate; that is,
it must not delay traffic unduly while deciding whether to allow it.
This consideration is one facet of the censor's sensistivity to
collateral damage caused by false positives:
mistakenly blocking or degrading non-circumvention traffic causes the censor
to incur some penalty, just as mistakenly allowing circumvention traffic does.
The censor must allow TLS connections; meek does not try to look like plaintext.

The user's computer, the third-party infrastructure (e.g., Google), and the Tor bridge
are all uncontrolled and uncompromised by the censor.
The user has a way to get a copy of the necessary client programs.

@@

We are running a paid instance of the web app on App Engine for use by the public.
The cost for bandwidth on App Engine is \$0.12 per gigabyte,
with one gigabyte free each day.
The total cost has so far been \$1.11, with bills of
\$0.09 in March,
\$0.73 in April,
and \$0.29 in May through May~12.
